Notes

### 2022-04-04 Notes.Rmd
update on ergms for several cases start buidling investor networks
update some figures and prelim results
some figs updates

Exponential random graph models:
- Include world governance indicators
- Inequality
- Triangles? Feedforward triangles -> theory on instability?
- Valued ergm with number of companes count on link weight?

>>>>

Exponential random graph models:
- Include world governance indicators
- Inequality
- Triangles? Feedforward triangles -> theory on instability?
- Valued ergm with number of companes count on link weight?
- Create network of investors combined for all cases
- Create investor - country (where investors are based)
- The later two should provide descriptive stats.

Experiment with the HH-Index: https://en.wikipedia.org/wiki/Herfindahl–Hirschman_index

Cannot make it bipartite because:
The following vertices appear in both columns:
	- Bnp Paribas
	- Oji Holdings Corporation
